Manuscript results

### 2024-02-05 04_analysis/control scenarios/Bryans SickKids data firstline/chart_audit_survival_new_controls_firstline.Rmd
upload results combo prices

```{r}
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = status) ~ 1, data = df)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = df,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = F,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in years', # Change X-axis label
  title      = "Survival curve for PFS",
  subtitle   = "Based on Kaplan-Meier estimates"
)
```

@@

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(df), replace=T)
  PFS_data_boot <- df[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "status", 
                     data = PFS_data_boot %>% as.data.frame(),
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_sk_firstline.RData")
```

>>>>

```{r}
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = status) ~ 1, data = df)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = df,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in years', # Change X-axis label
  title      = "Kaplan-Meier survival curve for PFS, Control arm",
  subtitle   = "Source: SickKids (first-line)"
)
```

@@

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(df), replace=T)
  PFS_data_boot <- df[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "status", 
                     data = PFS_data_boot %>% as.data.frame(),
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_sk_firstline_exp_100.RData")
```

### 2024-02-05 04_analysis/control scenarios/Erics firstline RCT/first_line_paper_survival.Rmd
updated
upload results combo prices

# 04 Digitized Data

@@

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
  title      = "Survival curve for PFS, Control arm",
  subtitle   = "Based on Kaplan-Meier estimates"
)
```

```{r}
surv_data$Time <- surv_data$Time/12 # change time in months to years
# times <- seq(0,5,by=1/12)
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods) 
```

@@

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("lnorm"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$`log-Normal`
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_firstline.RData")
```

@@

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
  title      = "Survival curve for PFS, Targeted arm",
  subtitle   = "Based on Kaplan-Meier estimates"
)
```

```{r}
surv_data$Time <- surv_data$Time/12
# times <- seq(0,5,by=1/12)
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods)
```

@@

```{r}
mods=c("exp", "llogis")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods=mods)
```

```{r}
N_sim <- 100
fitted_PFS_targeted <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline.RData")
```

>>>>

# Independent Reviewer

## 04 Digitized Data

@@

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
  title      = "Kaplan-Meier survival curve for PFS, Control arm (Independent Reviewer)",
  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
)
```

```{r}
# surv_data$Time <- surv_data$Time/12 # change time in months to years
IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
# times <- seq(0,5,by=1/12)
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods) 
```

@@

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("lnorm"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$`log-Normal`
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_firstline_lnorm_100.RData")
```

@@

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
title      = "Kaplan-Meier survival curve for PFS, Targeted arm (Independent Reviewer)",
  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
)
```

```{r}
IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
# times <- seq(0,5,by=1/12)
times <- 0:80
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods)
```

@@

```{r}
mods=c("exp", "lnorm")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods=mods)
```

```{r}
N_sim <- 100
fitted_PFS_targeted <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_exp_100.RData")
```

```{r}
N_sim <- 100
fitted_PFS_targeted <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("lnorm"))
  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$`log-Normal`
  print(i)
}
save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_lnorm_100.RData")
```

# Investigator Assessment

## 04 Digitized Data

```{r}
time_interval <- seq(0, 36, by = 2)
at_risk <- c(37,28,22,22,16,14,13,11,11,11,6,6,4,3,2,1,0,0,0)
surv_data <- read.csv("Eric NEJM investigator digitized.csv", header = T)
surv_data <- surv_data[surv_data$curve==1,]
surv_data$St <- surv_data$St/100
surv_data <- data.frame(k = 1:nrow(surv_data),
                        Time = surv_data$time,
                        Sk = surv_data$St)
write.table(surv_data, file = "first_line_PFS_curve_control_investigator.txt", row.names = F)
surv_data <- read.table("first_line_PFS_curve_control_investigator.txt", header = T)
surv_times <- surv_data$Time

n_risk_table <- create_at_risk_table(survival_time = surv_times,
                                     Years = time_interval,
                                     AtRisk = at_risk)
write.table(n_risk_table, "first_line_PFS_risktable_control_investigator.txt", row.names = F)
```

```{r, results="hide"}
# Create IPD and KM data for the PFS curves (there have been 99 events in the cohort)
digitise(surv_inp   = "first_line_PFS_curve_control_investigator.txt", 
         nrisk_inp  = "first_line_PFS_risktable_control_investigator.txt", 
         km_output  = "first_line_PFS_KM_control_investigator.txt", 
         ipd_output = "first_line_PFS_IPD_control_investigator.txt")

# Link the IPD files across the two arms of the trial for OS and PFS
IPD_PFS <- make.ipd(ipd_files = c("first_line_PFS_IPD_control_investigator.txt"), ctr = 1,
                    var.labs  = c("time","event","arm"))
IPD_PFS <- IPD_PFS %>% select(-arm)
```

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
  title      = "Kaplan-Meier survival curve for PFS, Control arm (Invesigator Assessment)",
  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
)
```

```{r}
# surv_data$Time <- surv_data$Time/12 # change time in months to years
IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
# times <- seq(0,5,by=1/12)
times <- 0:3
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods) 
```

```{r}
N_sim <- 100
fitted_PFS_chemo <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("lnorm"))
  fitted_PFS_chemo[[i]] <- fit_PFS$model.objects$models$`log-Normal`
  print(i)
}
save(fitted_PFS_chemo, file="fitted_PFS_control_firstline_investigator_lnorm_100.RData")
```

```{r}
time_interval <- seq(0, 36, by = 2)
at_risk <- c(73,68,68,67,58,52,47,39,38,27,24,18,13,11,5,5,1,1,0)
surv_data <- read.csv("Eric NEJM investigator digitized.csv", header = T)
surv_data$St <- surv_data$St/100
surv_data <- surv_data[surv_data$curve==2,]
surv_data <- data.frame(k = 1:nrow(surv_data),
                        Time = surv_data$time,
                        Sk = surv_data$St)
write.table(surv_data, file = "first_line_PFS_curve_targeted_investigator.txt", row.names = F)
surv_data <- read.table("first_line_PFS_curve_targeted_investigator.txt", header = T)
surv_times <- surv_data$Time

n_risk_table <- create_at_risk_table(survival_time = surv_times,
                                     Years = time_interval,
                                     AtRisk = at_risk)
write.table(n_risk_table, "first_line_PFS_risktable_targeted_investigator.txt", row.names = F)
```

```{r, results="hide"}
# Create IPD and KM data for the PFS curves (there have been 99 events in the cohort)
digitise(surv_inp   = "first_line_PFS_curve_targeted_investigator.txt",
         nrisk_inp  = "first_line_PFS_risktable_targeted_investigator.txt",
         km_output  = "first_line_PFS_KM_targeted_investigator.txt",
         ipd_output = "first_line_PFS_IPD_targeted_investigator.txt")

# Link the IPD files across the two arms of the trial for OS and PFS
IPD_PFS <- make.ipd(ipd_files = c("first_line_PFS_IPD_targeted_investigator.txt"), ctr = 1,
                    var.labs  = c("time","event","arm"))
IPD_PFS <- IPD_PFS %>% select(-arm)
```

```{r}
library(survival)
library(survminer)
# Kaplan-Meier fit for PFS
KM_PFS <- survfit(Surv(time = time, event = event) ~ 1, data = IPD_PFS)
# plot KM for PFS
ggsurvplot(
  KM_PFS,
  data       = IPD_PFS,
  size       = 1,                # change line size
  conf.int   = FALSE,            # Add confidence interval
  pval       = F,                # Add p-value
  risk.table = T,                # Add risk table
  risk.table.height = 0.25,      # Useful to change when you have multiple groups
  break.x.by = 2,
  ggtheme    = theme_bw(),       # Change ggplot2 theme
  xlab       = 'Time in months', # Change X-axis label
title      = "Kaplan-Meier survival curve for PFS, Targeted arm (Investigator Assessment)",
  subtitle   = "Source: Bouffet et al., (NEJM 2023)"
)
```

```{r}
IPD_PFS$time <- IPD_PFS$time/12 # change time in months to years
# times <- seq(0,5,by=1/12)
times <- 0:3
mods <- c("exp", "weibull", "gamma", "lnorm", "llogis", "gompertz" ,"rps")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods = mods)
```

```{r}
mods=c("exp", "lnorm", "llogis")
fit_PFS  <- fit.fun(time = "time", status = "event", data = IPD_PFS, times = times,
                    extrapolate = T, mods=mods)
```

```{r}
N_sim <- 100
fitted_PFS_targeted <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("exp"))
  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$Exponential
  print(i)
}
save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_investigator_exp_100.RData")
```

```{r}
N_sim <- 100
fitted_PFS_targeted <- list()
set.seed(1)
for (i in 1:N_sim) {
  ids <- sample(1:nrow(IPD_PFS), replace=T)
  PFS_data_boot <- IPD_PFS[ids,]
  fit_PFS <- fit.fun(time  = "time", status = "event", data = PFS_data_boot,
                     times = times, extrapolate = T, mods=c("lnorm"))
  fitted_PFS_targeted[[i]] <- fit_PFS$model.objects$models$`log-Normal`
  print(i)
}
save(fitted_PFS_targeted, file="fitted_PFS_targeted_firstline_investigator_lnorm_100.RData")
```

```{r}

```

### 2024-02-05 05_report/Manuscript_results_temp.Rmd
upload results combo prices

---
title: "Manuscript results"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
#rm(list = ls())
```

@@

```{r}
#fileloc <- here::here("04_analysis","output","scenarios")
#fileloc <- "/Users/davidrios/OneDrive - SickKids/tomacbook"
```

@@

```{R}
# model results 
#res_model <- list.files(paste0(fileloc, "/Scenario 1 life-time treatment", "/res_model"),full.names = TRUE)
res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:10]
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount30", "/res_model"),full.names = TRUE)

@@

tb2 <-df_model3  %>%
  filter(subset == "all") %>% 
  filter( !(Variable == "Cost" & discount == 0),
          !(Variable == "QALY" & discount == 0) ) %>%
  select(-Variable, - subset,-discount  ) %>% 
  rename(Variable = Type,
         Delta = delta,
         intervention = Targeted,
         control = SoC)

@@

# kable(tb2)
tb2a <- tb2 %>% 
  mutate(Variable = fct_recode(Variable, `Life-years` = "LY", 
                               QALY = "QALY",
                               `Total Cost` = "Total")) %>%
  select(Variable, intervention, control, Delta , rr)

pander(tb2a)
```

>>>>

---
title: "Manuscript results"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
#rm(list = ls())
options(scipen=999)
```

@@

```{r}
fileloc <- here::here("04_analysis","output","scenarios","basecase exp lifetime combo")
nn <- 50
```

@@

```{R}
# model results 
#res_model <- list.files(paste0(fileloc, "/Scenario 1 life-time treatment", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(here::here("04_analysis","output"), "/res_model"),full.names = TRUE)[1:5]
res_model <- list.files(paste0(fileloc, "/res_model"),full.names = TRUE)[1:nn]
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount20", "/res_model"),full.names = TRUE)
#res_model <- list.files(paste0(fileloc, "output/rad_after_prog2_lifetime_discount30", "/res_model"),full.names = TRUE)

@@

tb2 <-df_model3  %>%
  filter(subset == "all") %>% 
  filter( !(Variable == "Cost" & discount == 0),
          !(Variable == "QALY" & discount == 0) ) %>%
  select(-Variable, - subset,-discount  ) %>% 
  rename(Variable = Type,
         Delta = delta,
         intervention = Targeted,
         control = SoC) 
```

@@

# kable(tb2)
tb2a <- tb2 %>% 
  mutate(Variable = fct_recode(Variable, `Life-years` = "LY", 
                               QALY = "QALY",
                               `Total Cost` = "Total")) %>%
  #select(Variable, intervention, control, Delta , rr)
  select(Variable, intervention, control, Delta )
tb2a$Variable <- as.character(tb2a$Variable)
tb2a$Variable[tb2a$Variable=="Treatment"] <- "Targeted costs"
tb2a$Variable[tb2a$Variable=="PLGG"] <- "Non-Targeted PLGG related costs"
tb2a$Variable[tb2a$Variable=="AE"] <- "AE related costs"
tb2a$Variable[tb2a$Variable=="Radiation"] <- "Radiation costs"
tb2a$Variable <- factor(tb2a$Variable, levels = c("Life-years","QALY","Total Cost","Non-Targeted PLGG related costs",
                                                  "AE related costs","Targeted costs","Radiation costs"))
pander(tb2a)
```

```{r}
# Averaging cohort traces across simulation run
l_prop_df <- list.files(paste0(fileloc, "/trace"),full.names = TRUE)[1:nn]
prop_df  <- map_df(l_prop_df[1], readRDS) 
prop_df$cycle <- as.numeric(prop_df$cycle)
prop_df$intervention <- ifelse(prop_df$intervention == "Targeted", 1, 0)
prop_df <- apply(prop_df,2,as.numeric)
prop_df <- as.data.frame(prop_df)
prop_df <- prop_df %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
if (nn > 1) {
  for (i in 2:nn) {
    prop_df_i  <- map_df(l_prop_df[i], readRDS) 
    prop_df_i$cycle <- as.numeric(prop_df_i$cycle)
    prop_df_i$intervention <- ifelse(prop_df_i$intervention == "Targeted", 1, 0)
    prop_df_i <- prop_df_i %>% dplyr::select("cycle", "pre_prog", "auditory", "cardiovascular", "death_outside", 
                                             "death_plgg", "neurologic", "prog1", "SN", "stroke", "visual", "death_cardio",
                                             "prog2", "SN_gen", "death_SN", "death_stroke", "cardiovascular_gen",
                                             "stroke_gen", "intervention")
    prop_df_i <- apply(prop_df_i,2,as.numeric)
    prop_df_i <- as.data.frame(prop_df_i)
    prop_df <- prop_df + prop_df_i
  }
  prop_df <- prop_df/nn
}
prop_df$intervention <- ifelse(prop_df$intervention == 1, "Targeted", "SoC")

prop_long <- prop_df %>% select(cycle, pre_prog, prog1, prog2, death_plgg, intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(state=case_when(state=="pre_prog"~"Pre-progression",
                         state=="prog1" ~ "1st progression",
                         state=="prog2" ~ "2nd+ progression",
                         state=="death_plgg" ~ "PLGG-related death"),
         state=factor(state, levels=c("Pre-progression", "1st progression", "2nd+ progression", "PLGG-related death")),
         cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of PLGG States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG state") +
  scale_color_manual(values = c("green","orange","red","navy")) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, by = 10)) +
  #geom_hline(yintercept=0.4, linetype="dashed", color = "purple") +
  #geom_vline(xintercept=25, linetype="dashed", color = "purple") +
  theme_bw() +
  theme(legend.position = "right") + 
  facet_wrap(~intervention)
```

```{r}
# AEs
l_AE_df <- list.files(paste0(fileloc, "/AE_track"),
                      full.names = TRUE)[1:nn]
AE_df <- map_df(l_AE_df[1], readRDS) 
## Targeted
AE_df_Targeted <- AE_df %>% filter(intervention == "Targeted")
AE_prop_Targeted <-apply(AE_df_Targeted %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
df_AE_Targeted <- data.frame(cycle=0:960)
df_AE_Targeted$cycle <- as.factor(df_AE_Targeted$cycle)
for (i in 1:length(AE_prop_Targeted)){
  df_AE_prop <- as.data.frame(AE_prop_Targeted[[i]])
  colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted)[i])
  df_AE_Targeted <- df_AE_Targeted %>% left_join(df_AE_prop, by = c("cycle"))
}
df_AE_Targeted[1,-1] <- 0
df_AE_Targeted$cycle <- as.numeric(df_AE_Targeted$cycle)
df_AE_Targeted[is.na(df_AE_Targeted)] <- 0
if (nn == 1) {
  df_AE_Targeted$intervention <- "Targeted"
}

if (nn > 1) {
  for (i in 2:nn) {
    AE_df <- map_df(l_AE_df[i], readRDS) 
    AE_df_Targeted_i <- AE_df %>% filter(intervention == "Targeted")
    AE_prop_Targeted_i <-apply(AE_df_Targeted_i %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
    df_AE_Targeted_i <- data.frame(cycle=0:960)
    df_AE_Targeted_i$cycle <- as.factor(df_AE_Targeted_i$cycle)
    for (j in 1:length(AE_prop_Targeted_i)){
      df_AE_prop <- as.data.frame(AE_prop_Targeted_i[[j]])
      colnames(df_AE_prop) <- c("cycle",names(AE_prop_Targeted_i)[j])
      df_AE_Targeted_i <- df_AE_Targeted_i %>% left_join(df_AE_prop, by = c("cycle"))
    }
    df_AE_Targeted_i[1,-1] <- 0
    df_AE_Targeted_i$cycle <- as.numeric(df_AE_Targeted_i$cycle)
    df_AE_Targeted_i[is.na(df_AE_Targeted_i)] <- 0
    df_AE_Targeted <- df_AE_Targeted + df_AE_Targeted_i
  }
  df_AE_Targeted <- df_AE_Targeted/nn
  df_AE_Targeted$intervention <- "Targeted"
}
## SoC
AE_df_SoC <- AE_df %>% filter(intervention == "SoC")
AE_prop_SoC <-apply(AE_df_SoC %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
df_AE_SoC <- data.frame(cycle=0:960)
df_AE_SoC$cycle <- as.factor(df_AE_SoC$cycle)
for (i in 1:length(AE_prop_SoC)){
  df_AE_prop <- as.data.frame(AE_prop_SoC[[i]])
  colnames(df_AE_prop) <- c("cycle",names(AE_prop_SoC)[i])
  df_AE_SoC <- df_AE_SoC %>% left_join(df_AE_prop, by = c("cycle"))
}
df_AE_SoC[1,-1] <- 0
df_AE_SoC$cycle <- as.numeric(df_AE_SoC$cycle)
df_AE_SoC[is.na(df_AE_SoC)] <- 0
if (nn == 1) {
  df_AE_SoC$intervention <- "SoC"
}

if (nn > 1) {
  for (i in 2:nn) {
    AE_df <- map_df(l_AE_df[i], readRDS) 
    AE_df_SoC_i <- AE_df %>% filter(intervention == "SoC")
    AE_prop_SoC_i <-apply(AE_df_SoC_i %>% dplyr::select(-intervention), 2, function(x){prop.table(table(x))})
    df_AE_SoC_i <- data.frame(cycle=0:960)
    df_AE_SoC_i$cycle <- as.factor(df_AE_SoC_i$cycle)
    for (j in 1:length(AE_prop_SoC_i)){
      df_AE_prop <- as.data.frame(AE_prop_SoC_i[[j]])
      colnames(df_AE_prop) <- c("cycle",names(AE_prop_SoC_i)[j])
      df_AE_SoC_i <- df_AE_SoC_i %>% left_join(df_AE_prop, by = c("cycle"))
    }
    df_AE_SoC_i[1,-1] <- 0
    df_AE_SoC_i$cycle <- as.numeric(df_AE_SoC_i$cycle)
    df_AE_SoC_i[is.na(df_AE_SoC_i)] <- 0
    df_AE_SoC <- df_AE_SoC + df_AE_SoC_i
  }
  df_AE_SoC <- df_AE_SoC/nn
  df_AE_SoC$intervention <- "SoC"
}

df_AE <- rbind(df_AE_Targeted, df_AE_SoC)

prop_long <- df_AE %>% select(cycle,auditory,cardiovascular,neurologic,SN,stroke,visual,intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of PLGG-related AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "PLGG-related AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> a

prop_long <- df_AE %>% select(cycle,SN_gen,cardiovascular_gen,death_outside,death_SN,stroke_gen,death_cardio,death_stroke, 
                                intervention) %>%
  tidyr::pivot_longer(-c(cycle,intervention), names_to = "state", values_to = "proportion") %>%
  mutate(cycle=cycle/12)
ggplot(data = prop_long, aes(x = cycle, y = proportion, color = state, group = state)) +
  geom_line() +
  labs(title = "Trace Plot of Other AE States Across Cycles",
       x = "Year",
       y = "Proportion",
       color = "Other AE states") +
  theme_bw() +
  theme(legend.position = "right") +
  facet_wrap(~intervention) -> b
grid.arrange(a,b, nrow=2, ncol=1)
```
